Open-source landscape for 3D CSEM modelling

### 2020-10-11 manuscript/Manuscript.tex
Updates from Overleaf

%
\tabl[bthp]{comp-layered}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}{
  \centering
\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
  \toprule
  %
       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
  \midrule
  %
  \custem & 24 &   118 &  97.8 & 1530808 \\ % dof: 3061616 / 2 (Real+Imag -> Complex)
  \emg3d  &  1 &   116 &   0.4 & 4813216 \\
  \petgem & 24 &   252 & 151.7 & 2455868 \\
  \simpeg &  4 & 10089 & 280.3 & 4813216 \\ % nprocs: 1*4 threads
  %
  \bottomrule
\end{tabular}}%
%

@@

The corresponding required runtime and memory are listed in Table~\ref{tbl:comp-block}.
%
\tabl[bthp]{comp-block}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the block model.}{
  \centering
\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
\toprule
  %
       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
  \midrule
  %
  \custem & 24 &   158 & 115.9 & 1654242 \\ % dof: 3308484 / 2  (Real+Imag -> Complex)
  \emg3d  &  1 &   115 &   0.4 & 4813216 \\
  \petgem & 24 &    238 &  152.8 & 2455868 \\
  \simpeg &  4 & 10295 & 280.4 & 4813216 \\ % nprocs: 1*4 threads
  %
  \bottomrule
\end{tabular}}%
%

@@

\plot*{results-marlim_medium}{width=\textwidth}{Additional zoom “medium”; which ones should we use? (Vertical exaggeration: 1.33)}
\plot*{results-marlim_small}{width=\textwidth}{Additional zoom “small”; which ones should we use? (Vertical exaggeration: 4.0)}
%
\tabl[bthp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}{
  \centering
\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
  \toprule
  %
       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
  \midrule
  %
  \custem & 64 & 4034 & 522.7 & 4539474 \\ % dof: 9078948 / 2 (Real+Imag -> Complex)
  \emg3d  &  1 & 1200 &   0.5 & 5998992 \\
  \petgem & 96 &  524 & 175.4 & 1918106 \\
  \simpeg &  4 &  422 &  12.8 &  720146 \\ % nprocs: 1*4 threads
  %
  \bottomrule
\end{tabular}}%
%
\itodo{Update nc-file of custEM and PETGEM for new CPU/RAM.}

>>>>

%
\tabl[bthp]{comp-layered}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}{
  \centering
\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
  \toprule
  %
       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
  \midrule
  %
  \custem & 24 &   118 &  97.8 & 1531824 \\ % dof: 3063648 / 2 (Real+Imag -> Complex)
  \emg3d  &  1 &   116 &   0.4 & 4813216 \\
  \petgem & 24 &   252 & 151.7 & 2455868 \\
  \simpeg &  4 & 10089 & 280.3 & 4813216 \\ % nprocs: 1*4 threads
  %
  \bottomrule
\end{tabular}}%
%

@@

The corresponding required runtime and memory are listed in Table~\ref{tbl:comp-block}.
%
\tabl[bthp]{comp-block}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the block model.}{
  \centering
\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
\toprule
  %
       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
  \midrule
  %
  \custem & 24 &   158 & 115.9 & 1646736 \\ % dof: 3293472 / 2  (Real+Imag -> Complex)
  \emg3d  &  1 &   115 &   0.4 & 4813216 \\
  \petgem & 24 &    238 &  152.8 & 2455868 \\
  \simpeg &  4 & 10295 & 280.4 & 4813216 \\ % nprocs: 1*4 threads
  %
  \bottomrule
\end{tabular}}%
%

@@

\plot*{results-marlim_medium}{width=\textwidth}{Additional zoom “medium”; which ones should we use? (Vertical exaggeration: 1.33)}
\plot*{results-marlim_small}{width=\textwidth}{Additional zoom “small”; which ones should we use? (Vertical exaggeration: 4.0)}
%
\tabl[bthp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}{
  \centering
\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
  \toprule
  %
       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
  \midrule
  %
  \custem & 64 &  872 & 230.1 & 1918106 \\ % dof: 3836212 / 2 (Real+Imag -> Complex)
  \emg3d  &  1 & 1200 &   0.5 & 5998992 \\
  \petgem & 96 &  524 & 175.4 & 1918106 \\
  \simpeg &  4 &  422 &  12.8 &  720146 \\ % nprocs: 1*4 threads
  %
  \bottomrule
\end{tabular}}%
%
\itodo{Update nc-file of custEM and PETGEM for new CPU/RAM.}

\paragraph{TODOs:}
Figure \ref{fig:results-marlim_allmodels} is just added; integrate properly. Also, the following info should be integrated:
\begin{itemize}
    \item Model interpolation: \simpeg and \emg3d use volume averaging on log10(rho)-space; \custem and \petgem use linear interpolation on log10(rho)-space.
    \item Fields interpolation: \simpeg uses ???\mycom[DW]{Lindsey, what did you use in the end?}; \emg3d uses spline interpolation; the FE codes custEM and PETGEM use the second-order basis functions for the interpolation within elements. 
\end{itemize}
\plot*{results-marlim_allmodels}{width=\textwidth}{TODO}
